### 2016-06-09 conclusion.tex
some edits to address reviewer concerns

Nevertheless, Theorem 5 in \cite{Raj:suspension1991} could be useful for handling self-suspending tasks (that do not use suspension-based locks) if there exist \emph{efficient} schedulability tests for the corresponding deferrable task systems or the period enforcer algorithm. However, such tests have not been found yet and the development of a precise and efficient schedulability test for self-suspending tasks remains an open problem.

>>>>

Nevertheless, the period enforcer algorithm \emph{per se}, and Theorem 5 in \cite{Raj:suspension1991},  could still prove to be useful for handling self-suspending tasks (that do not use suspension-based locks) if  \emph{efficient} schedulability tests or methods for constructing sets of single-segment deferrable tasks can be found. However, such tests or transformations have not yet been found  and the development of a precise and efficient schedulability test for self-suspending tasks remains an open problem.

### 2016-06-09 locking.tex
some edits to address reviewer concerns

Notably, the examples in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} assume a shared-memory locking protocol: once a lock is granted, tasks execute their own critical sections, on their assigned processors. One may wonder whether  effects similar to those described in in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} can also occur under \emph{distributed} real-time locking protocols such as the DPCP~\cite{RSL:88} or the DFLP~\cite{Br:13,Br:14}, where critical sections may be executed on dedicated \emph{synchronization processors}. In this case, the self-suspension occurs on the task's \emph{application processor}, which is different from the (remote) synchronization processor on which the critical section is executed. This separation allows employing period enforcement  only on application processors (while avoiding it on synchronization processors) without incurring the feedback cycle between blocking times and self-suspension times highlighted in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2}. However, period enforcement still invalidates all existing blocking analyses for distributed real-time semaphore protocols~\cite{RSL:88,Raj:91,Br:13} because it artificially increases blocking times if tasks contain multiple accesses to shared resources.

>>>>

Notably, the examples in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} assume a \emph{shared-memory} locking protocol: once a lock is granted, tasks execute their own critical sections, on their assigned processors. One may wonder whether  effects similar to those described in in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} can also occur under \emph{distributed} real-time locking protocols such as the DPCP~\cite{RSL:88} or the DFLP~\cite{Br:13,Br:14}, where critical sections may be executed on dedicated \emph{synchronization processors}. In this case, the self-suspension occurs on the task's \emph{application processor}, which is different from the (remote) synchronization processor on which the critical section is executed. This separation allows employing period enforcement  only on application processors (while avoiding it on synchronization processors) without incurring the feedback cycle between blocking times and self-suspension times highlighted in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2}. However, period enforcement still invalidates all existing blocking analyses for distributed real-time semaphore protocols~\cite{RSL:88,Raj:91,Br:13} because it artificially increases blocking times if tasks contain multiple accesses to shared resources.

As a third possible interpretation in the shared-memory case, one could also exclude critical sections from period enforcement such that only the rest of the computation segment \emph{after} a critical section is subject to period enforcement (i.e., making critical sections immediately eligible to execute).\footnote{This interpretation does not fit the assumptions stated in~\cite{Raj:suspension1991,Raj:91}.} As in the case of distributed semaphore protocols, this interpretation breaks the feedback cycle highlighted in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2}, but still invalidates all existing blocking analyses as it artificially inflates the synchronization delay, just as if a single remote critical section could effectively block a job multiple times.
